\documentclass[11pt,usenames, dvipsnames]{article}

\input{Cv_structure.tex}        % Include file setting document structure and style
\usepackage[final]{pdfpages}           % Attention: clash for package xcolor in CV_structure.tex and pdfpages; set global options usenames and dvpsnames, then load input before pdfpages
\usepackage{url}

\pagenumbering{gobble}          % No number footpate

\title{\bfseries Ensor Palacios -- Curriculum Vitae}

\begin{document}
\date{\vspace{5ex}}   %no date
\maketitle
\vspace{-70pt}
%{\large \bfseries Ensor Rafael Palacios}\newline
\medskip

University of Bristol -- Integrative Epidemiology Unit.\newline
Beacon House, Queens Road, Bristol, BS8 1QU, UK\newline

Mobile: +44 (0)775 486 7735\newline
email: ensorrafael.palacios@bristol.ac.uk\newline 
       ensorrafael.palacios@gmail.com\newline

% email: \href{mailto:ensorrafael.palacios@bristol.ac.uk}{mailto:ensorrafael.palacios@bristol.ac.uk}\newline 
%        \href{mailto:ensorrafael.palacios@gmail.com}{mailto:ensorrafael.palacios@gmail.com}\newline

%\vspace{0.8cm}
\vspace{.35cm}

{\large \bfseries \color{color_64493} Education}\newline
\vspace{1pt}

\years{\bfseries 2018-2023} {\bfseries Phd}: University of Bristol, Wellcome Neural Dynamics Programme.\newline 
\vspace{-5pt}

\years{\bfseries 2015-2017} {\bfseries Master}: University of Padua, Cognitive Neuroscience and Clinical Neuropsychology (Department of Psychology). 110/110 \emph{cum laude}.\newline
\vspace{-5pt}

\years{\bfseries 2012-2015} {\bfseries Bachelor}: University of Padua, Cognitive Psychology and Psychobiology (Department of Psychology). 106/110.\newline
\vspace{-5pt}

%\years{\bfseries 2006-2011} {\bfseries High school degree}: Liceo Brocchi, scientific studies, Bassano del Grappa. 68/100. 

\vspace{1cm}

{\large \bfseries \color{color_64493} Projects}\newline
\vspace{1pt}

\years{\bfseries 2024-\newline present} {\bfseries Effects of air pollution on dementia}
\newline Postdoctoral transition fellowship: investigating the relationship between air pollution on dementia in the UK Biobank cohort; MRC Integrative Epidemiology Unit,
University of Bristol.
\newline Supervisor: Kate Tilling.

\vspace{7pt}

\years{\bfseries 2018-2023} {\bfseries Cerebellar neuronal dynamics}
\newline PhD project: excitatory-inhibitory balance and information processing in the cerebellar cortex; University of Bristol.
\newline Supervisors: Conor Houghton, Paul Chadderton.

\vspace{7pt}

\years{\bfseries 2018-2018} {\bfseries Neuronal self-organisation}
\newline UCL internship: simulations of neural network self-organisation under the free energy principle; Wellcome Trust Centre for Human Neuroimaging (UCL). 
\newline Supervisor: Karl Friston.

\vspace{7pt}

\years{\bfseries 2017-2017} {\bfseries Biological self-organisation}
\newline Master dissertation: simulations of biological self-organisation under the free energy principle; Wellcome Trust Centre for Human Neuroimaging (UCL).
\newline Supervisor: Karl Friston.

\vspace{7pt}

\years{\bfseries 2015-2015} {\bfseries Psychophysics of visual motion}
\newline Bachelor dissertation: neural correlates of visual motion perception using tDCS stimulation and EEG recordings; University of Padua.
\newline Supervisor: Gianluca Campana.

\newpage
\vspace*{1cm}

{\large \bfseries \color{color_64493} Awards}\newline
\vspace{1pt}

\years{\bfseries 2024} Wellcome Trust funded Neural Dynamics Transition Fellowship
\vspace{7pt}

\years{\bfseries 2018} Wellcome Trust PhD Studentship
\vspace{7pt}

\years{\bfseries 2018} Erasmus scholarship
\vspace{7pt}

\years{\bfseries 2017} Erasmus scholarship
\vspace{7pt}

\vspace{1cm}

{\large \bfseries \color{color_64493} Programming experience}
\vspace{10pt}

Matlab (internship)
\vspace{7pt}

Python (Phd)
\vspace{7pt}

R (postdoc)

\vspace{1cm}

{\large \bfseries \color{color_64493} Publications}
\vspace{10pt}

{\bfseries Palacios E. R.}, Chadderton P., Friston k., Houghton C., Cerebellar state estimation enables resilient coupling
        across behavioural domains, Scientific Reports, 2024 \url{https://www.nature.com/articles/s41598-024-56811-x}
\vspace{7pt}

{\bfseries Palacios E. R.}, Houghton C. and Chadderton P., The role of Golgi cells in cerebellar cortical transformation. 
        SFN poster, 2022. \url{https://zenodo.org/record/7304821#.Y4SSiDPP2V4}.
\vspace{7pt}

{\bfseries Palacios E. R.}, Houghton C.* and Chadderton P.*, Accounting for uncertainty: inhibition for neural inference in
        the cerebellum, Proceedings of the Royal Society B, 2021. \url{https://doi.org/10.1098/rspb.2021.0276}.
\vspace{7pt}

{\bfseries Palacios E.R.}, Isomura T., Parr T., Friston K., The emergence of synchrony in networks of mutually inferring
        neurons, Scientific Reports, 2019 \url{https://doi.org/10.1038/s41598-019-42821-7}.
\vspace{7pt}

{\bfseries Palacios E. R.}, Razi A., Parr T., Kirchhoff M., Friston K., On Markov blankets and hierarchical self-organisation, Journal
        of Theoretical Biology, 2020 \url{https://doi.org/10.1016/j.jtbi.2019.110089}.
\vspace{7pt}

Kirchhoff M., Parr T., {\bfseries Palacios E. R.}, Friston K. and Kiverstein J., The Markov blankets of life: autonomy, active
        inference and the free energy principle, Journal of The royal society interface, 2018 \url{http://doi.org/10.1098/rsif.2017.0792}.
\vspace{1cm}

* equal contribution

\end{document}
